ms_tables

### 2018-01-22 man/ms_tables.Rmd
update figures
update tables

@@

### Table R1

```{r, echo=FALSE}

dffs <- dff_bai %>% bind_rows(dff_evi)

>>>>

```{r, echo=FALSE}
show_text <- FALSE
```

```{r echo=FALSE, results='asis', eval=show_text}
cat("
# Lista de tablas

# Table 1 
* topograficos, y dendro summary

# Table 2 ANOVAS resilience BAI and EVI

")
```

## Table 1. Dendro summary statistics 
```{r, echo=FALSE, include = FALSE}
df <- read.csv(here("/out/anovas_resilience/huber_evi", "trimmed_anovas.csv"), header = TRUE)

## Table 2. Robust ANOVAS (F-value)
```{r, echo=FALSE, include = FALSE}

@@

## Table 2

```{r, echo=FALSE}
# table 2 (r1)
dffs <- dff_bai %>% bind_rows(dff_evi)
